ST563 Final Project

### 2021-04-30 DRAFT.Rmd
Corrected a typo.

# Plot the Cp, BIC, R^2, RSS results in one plot
par(mfrow = c(2,2))
plot(smre$cp, xlab = "# of Preds", ylab = "Cp")
points(which.min(smre$cp), smre$cp[which.min(smre$cp)], pch = 8, col = "#CC0000")
plot(smre$bic, xlab = "# of Preds", ylab = "BIC")
points(which.min(smre$bic), smre$bic[which.min(smre$bic)], pch = 8, col = "#CC0000")
plot(smre$adjr2, xlab = "# of Preds", ylab = "Adjusted R^2")
points(which.max(smre$adjr2), smre$adjr2[which.max(smre$adjr2)], pch = 8, col = "#CC0000")
plot(smre$rss, xlab = "# of Preds", ylab = "Training RSS")
points(which.min(smre$rss), smre$rss[which.min(smre$rss)], pch = 8, col = "#CC0000")

@@

Based on cross validation, the random forest model for regression using two randomly-selected variables considered at each split was selected. This model produced a test error rate of `r round(rf.reg.test_err,4)`.

>>>>

# Plot the Cp, BIC, R^2, RSS results in one plot
par(mfrow = c(2,2))
plot(smre$cp, xlab = "# of Preds", ylab = "Cp")
points(which.min(smre$cp), smre$cp[which.min(smre$cp)], pch = 8, col = "#CC0000")
plot(smre$bic, xlab = "# of Preds", ylab = "BIC")
points(which.min(smre$bic), smre$bic[which.min(smre$bic)], pch = 8, col = "#CC0000")
plot(smre$adjr2, xlab = "# of Preds", ylab = "Adjusted R^2")
points(which.max(smre$adjr2), smre$adjr2[which.max(smre$adjr2)], pch = 8, col = "#CC0000")
#plot(smre$rss, xlab = "# of Preds", ylab = "Training RSS")
#points(which.min(smre$rss), smre$rss[which.min(smre$rss)], pch = 8, col = "#CC0000")

@@

Based on cross validation, the random forest model for regression using two randomly-selected variables considered at each split was selected. This model produced a test RMSE of `r round(rf.reg.test_err,4)`.
